\documentclass[A4paper, 12pt, british, reqno]{amsart}

\input{preamble} % Content described in README.md

% Math operators
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\End}{End}
\DeclareMathOperator{\Ext}{Ext}
\DeclareMathOperator{\Aut}{Aut}
\DeclareMathOperator{\Sym}{Sym}
\DeclareMathOperator{\Spec}{Spec}
\DeclareMathOperator{\Proj}{Proj}
\DeclareMathOperator{\Pic}{Pic}
\DeclareMathOperator{\rk}{rk}
\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator{\pr}{pr}
\DeclareMathOperator{\ad}{ad}
\DeclareMathOperator{\GL}{GL}
\let\div\relax
\DeclareMathOperator{\div}{div}
\DeclareMathOperator{\SO}{SO}
\DeclareMathOperator{\SU}{SU}
\let\U\relax
\DeclareMathOperator{\U}{U}
\DeclareMathOperator{\SL}{SL}
\DeclareMathOperator{\su}{\mathfrak{su}}
\DeclareMathOperator{\so}{\mathfrak{so}}
\let\Im\relax
\DeclareMathOperator{\Im}{Im}
\DeclareMathOperator{\Ker}{Ker}
\DeclareMathOperator{\ch}{ch}
\DeclareMathOperator{\td}{td}

% Other commands
\newcommand{\ot}{\otimes}
\newcommand{\op}{\oplus}
\newcommand{\dual}{^{\vee}}
\newcommand{\act}{\rotatebox[origin=c]{-120}{$\circlearrowright$}}
\newcommand{\Diff}{\mathbf{Diff}}
\newcommand{\Grp}{\mathbf{Grp}}
\renewcommand{\X}{\mathfrak{X}}
\newcommand{\g}{\mathfrak{g}}
\renewcommand{\u}{\mathfrak{u}}
\newcommand{\prp}{^{\perp}}
\newcommand{\1}{\mathbbm{1}}

\begin{document}

\maketitle

\begin{abstract}
    We introduce the stability condition for Higgs bundles and discuss the Hitchin--Kobayashi correspondence \cite[\S 3 and \S 4]{hit87a}.
\end{abstract}

\tableofcontents

\begin{center}
\textcolor{gray}{---parts in gray will be omitted during the talk---}
\end{center}

\section{Introduction}

Let $M$ be a compact Riemann surface of genus $g$.
Fix a Hermitian metric on $M$ normalized to unit volume, \textcolor{gray}{i.e.~such that
\[ \operatorname{Vol}(M)=\int_{M}\w_{M}=1, \]
where $\w_{M}\in A^{1,1}(M)$ is the corresponding Kähler form \cite[Beginning of \S 3.3]{voi02} and $\operatorname{Vol}(M)$ is the Riemannian volume \cite[Lemma 3.8]{voi02}.}

Hitchin's equations \cite[(1.3)]{hit87a} were originally stated for principal $G$-bundles over $M$, but for $G=\SO(3)$ they reduce to the study of rank $2$ complex vector bundles on $M$ \cite[Beginning of \S 2]{hit87a}.
So let $E$ be a rank $2$ complex vector bundle on $M$ and fix a Hermitian metric $h$ on $E$ \cite[Proposition 4.1.4]{huy05}.
A solution to Hitchin's equations in this set up consists of a unitary connection $\nabla \colon A^{0}(E)\to A^{1}(E)$ and a traceless endomorphism valued $(1,0)$-form $\Phi\in A^{1,0}(\End_{0}(E))$ such that
\begin{equation}\label{eqn:hitchin}
    \begin{cases}
	F+[\Phi,\Phi^{*}]=-2\pi i \mu(E)\1_{E}\w_{M}, \\
	\nabla^{0,1}\Phi=0.
    \end{cases}
\end{equation}
\textcolor{gray}{%
About the notation:
\begin{itemize}
    \item $F\colon A^{0}(E)\to A^{2}(E)$ is the curvature of the connection $\nabla$.
    \item $\Phi$ can be locally written as $\phi dz$, where $\phi$ is a local section of $\End_{0}(E)$ and $z$ is a local holomorphic coordinate.
	Then $\Phi^{*}$ can be locally written as $\phi^{*} d\bar{z}$, where $\phi^{*}$ is the $h$-adjoint of $\phi$; and $[\Phi,\Phi^{*}]$ can be locally written as $[\phi,\phi^{*}]dz\wedge d\bar{z}$.
    \item $\mu(E)$ is the slope of the vector bundle $E$, defined as $\frac{1}{2}\deg(\Lambda^{2}E)$.
    \item $\1_{E}\in A^{0}(\End(E))$ denotes the identity endomorphism.
    \item $\nabla^{0,1}\colon A^{0}(E)\to A^{0,1}(E)$ denotes the $(0,1)$-part of $\nabla$.
    \item We followed the sign convention in \cite[(4.17)]{wen16}.
	Other references, such as \cite[p.~38]{tho05}, follow the opposite sign convention.
\end{itemize}
}

\textcolor{gray}{%
Since $d\bar{z}\wedge d\bar{z}=0$, the integrability condition is automatic on a Riemann surface, so $\nabla^{0,1}$ defines a holomorphic structure on $E$ \cite[Theorem 2.6.26]{huy05}.
We can regard $\Phi$ as a smooth section of $\End_{0}(E)\ot K$.
The condition $\nabla^{0,1}\Phi=0$ then translates into $\Phi$ being a holomorphic section of $\End_{0}(E)\ot K$.
This in turn can be regarded as a holomorphic morphism $E\to E\ot K$.
Moreover, if $(E,\Phi)$ is a solution which does not degenerate into a direct sum of line bundles, then every line bundle $L\subseteq $ such that $\Phi(L)\subseteq L\ot K$ verifies $\mu(L)<\mu(E)$ \cite[Proposition 4.2.16]{wen16}.
This condition is what we will call \textit{stability} of the Higgs bundle $(E,\Phi)$.
}

The existence proof in \cite[(4.3)]{hit87a} is based on Donaldson's proof of the existence of connections with constant central curvature on stable vector bundles \cite{don83}, which was discussed in Tanuj's talk.
The difference between the two settings is the introduction of the Higgs field $\Phi$, so the main goal of this talk will be to understand stability of such pairs $(E,\Phi)$.
At the end of the talk we will see how to modify Donaldson's proof to produce solutions to Hitchin's equations.

\section{Stability of Higgs bundles}

\begin{unota}
    In this first section, all vector bundles, morphisms and sections are assumed to be holomorphic.
    We will often go back and forth between vector bundles $E$ and their sheaves of sections $\E$.
    We denote the set of rank $2$ vector bundles on $M$ by $\Vec_{2}(M)$.
\end{unota}

\begin{udefn}[Higgs bundle]
    A \textit{Higgs bundle} on $M$ is a pair $(E,\Phi)$, where $E\in \Vec_{2}(M)$ and $\Phi\in H^{0}(M,\sEnd_{0}(\E)\ot \sK)$.
    We call $\Phi$ a \textit{Higgs field} on $E$.
\end{udefn}

\begin{urem}
    Using the canonical isomorphisms
    \[ H^{0}(M,\sEnd(\E)\ot \sK)\cong \Hom(\O,\E\dual \ot \E\ot \sK)\cong \Hom(\E,\E\ot \sK) \]
    we may identify $\Phi$ with a morphism $\Phi\colon E\to E\ot K$.
\end{urem}

\begin{udefn}[Stability]
    A Higgs bundle $(E,\Phi)$ is said to be \textit{stable} if for every $\Phi$-invariant line bundle $L\subseteq E$ we have $\mu(L)<\mu(E)$, where $\Phi$-invariance means that $\Phi(L)\subseteq L\ot K$.
\end{udefn}

\begin{urem}
    $(E,0)$ is stable if and only if $E$ is stable in the usual sense.
\end{urem}

\begin{cexe}{A}
    There are no stable Higgs bundles on $\P^{1}$.
    [\textit{Hints below}\footnote{Grothedieck's theorem allows us to write $\Phi$ as a matrix.
    What can we say about each entry?
    The solution can be found in \cite[(3.2) (iii)]{hit87a}}]
\end{cexe}

\begin{lm}\label{lm:traceless}
    For every $E\in \Vec_{2}(E)$ there is a short exact sequence
    \[ 0\to \O\to \sEnd(\E)\to \sEnd_{0}(\E)\to 0 \]
    in which the left hand side is the trivial line bundle generated by $\1_{E}$.
    In particular, by Hirzebruch--Riemann--Roch,
    \[ \chi(\sEnd_{0}(\E)\ot \sK)=3g-3. \]
    \begin{proof}
	Over $x\in M$ we consider the projection $\End(E_{x})\to \End_{0}(E_{x})$ is given by
	\[ \phi\mapsto \phi-\frac{\tr(\phi)}{2}\1_{E_{x}}. \]
	The endomorphisms in the kernel are precisely the multiples of the identity, and this fiber-wise description globalizes to the desired short exact sequence.	
	\textcolor{gray}{%
	For the Chern class computation we use the axioms in \cite[Appendix A]{har77}.
	We have
	\[ c_{1}(\sEnd_{0}(\E))=c_{1}(\sEnd(\E))=c_{1}(\E\dual\ot\E)=0, \]
	therefore
	\[ \ch(\sEnd_{0}(\E)\ot \sK)=3+c_{1}(\sEnd_{0}(\E))+3c_{1}(\sK)=3+3c_{1}(\sK). \]
	We also have
	\[ \td(\sK\dual)=1-\frac{c_{1}(\sK)}{2}, \]
	so multiplying the two expressions we obtain
	\[ \ch(\sEnd_{0}(\E)\ot \sK)\td(\sK\dual)=3+\frac{3}{2}c_{1}(\sK). \]
	Since $\deg(c_{1}(\sK))=2g-2$, we deduce that
	\[ \deg(\ch(\sEnd_{0}(\E)\ot\sK)\td(\sK\dual))_{1}=3g-3. \]
	The second assertion follows now from Hirzebruch--Riemann--Roch \cite[Theorem A.4.1]{har77}.
	}
    \end{proof}
\end{lm}

\begin{unota}
    We define the following subsets of $\Vec_{2}(M)$:
    \begin{itemize}
	\item $\bfS:=\{ E\in \Vec_{2}(M)\mid \exists \Phi \text{ such that }(E,\Phi)\text{ is stable}\}$.
	\item $\bfA:=\{ E\in \Vec_{2}(M)\mid \text{for general }\Phi\text{ there is no invariant }L \}$.
	\item $\bfB:=\{ E\in \Vec_{2}(M)\mid \exists L\text{ invariant for all }\Phi\}$.
    \end{itemize}
\end{unota}

\begin{lm}\label{lm:twocases}
    If $g\geqslant 2$, then
    \[ \Vec_{2}(M)=\bfA\sqcup \bfB. \]
    \begin{proof}
	Let $\pi\colon \P(E)\to M$ be the projectivization of our rank $2$ vector bundle and let $O(-1)\to \P(E)$ denote the tautological line bundle, whose fiber over $[v]\in \P(E)$ is the line $\{\lambda v\mid \lambda\in \C\}\subseteq E_{\pi([v])}$ spanned by $v$.
	Let $O(l):=O(-1)^{\ot (-l)}$.
	If $\F$ is a sheaf on $\P(E)$, we denote $\F(l):=\F\ot \O(l)$, where $\O(l)$ denotes the sheaf of sections of $O(l)$.
	Using the relative $\Proj$ construction we can write $\P(E)=\P(\E\dual):=\Proj_{M}(S(\E\dual))$, so \cite[Exercise III.8.4]{har77} implies that
	\[ \pi_{*}\O(l)=\begin{cases} S^{l}(\E\dual) & \text{ if } l\geqslant 0, \\
	    0 & \text{ if }l<0.
	\end{cases}
	\]

	Let $x\in M$.
	Given $\phi\in \End(E_{x})$, we define the quadratic form $v\mapsto \phi(v)\wedge v$ with values in $\Lambda^{2}E_{x}$, which corresponds to an element in $S^{2}(E_{x}\dual)\ot\Lambda^{2}E_{x}$.
	The resulting quadratic form is trivial precisely when $\phi=\lambda\1_{E_{x}}$ for some $\lambda\in \C$, so by \Cref{lm:traceless} we obtain an injective homomorphism $\End_{0}(E_{x})\to S^{2}(E_{x}\dual)\ot \Lambda^{2}E_{x}$.
	Both vector spaces have the same dimension, so this must be an isomorphism.
	These isomorphisms globalize to an isomorphism $\End_{0}(E)\cong S^{2}(E\dual)\ot \Lambda^{2}E$, hence we obtain an isomorphism
	\[ \sEnd_{0}(\E)\ot \sK\cong \pi_{*}\O(2)\ot (\Lambda^{2}\E)\ot \sK. \]
	The projection formula yields now an isomorphism $\sEnd_{0}(\E)\ot \sK\cong \pi_{*}(\pi^{*}(\sK\ot \Lambda^{2}\E)(2))$, hence an isomorphism
	\[ \psi \colon H^{0}(M,\sEnd_{0}(\E)\ot \sK)\cong H^{0}(\P(E),\pi^{*}(\sK\ot \Lambda^{2}\E)(2)). \]
	Let now $\Phi\in H^{0}(M,\sEnd_{0}(\E)\ot \sK)$.
	By construction of $\psi$, a line bundle $L\subseteq E$ is $\Phi$-invariant if and only if $\psi(\Phi)$ vanishes at all $[v]\in \P(L)\subseteq \P(E)$.
	In other words, $L$ is $\Phi$-invariant if and only if $\sigma(M)\subseteq \div(\psi(\Phi))$, where $\div(-)$ denotes the divisor of zeros of a section and $\sigma\colon M=\P(L)\to \P(E)$ is the section induced by $L\subseteq E$.

	Suppose now that $\Phi\in H^{0}(M,\sEnd_{0}(\E)\ot \sK)$ is not nilpotent and let $L\subseteq E$ be a $\Phi$-invariant line bundle.
	Over a general point $x\in M$ the corresponding traceless endomorphism $\phi\in \End_{0}(E_{x})$ is diagonalizable, so we can find some eigenvector $v\in E_{x}\setminus L_{x}$ in an eigenspace other than $L_{x}$.
	This gives us a point $[v]\in \P(E)\setminus \sigma(M)$ on which $\psi(\Phi)$ vanishes.
	Hence $\sigma(M)$ is a proper irreducible component of the divisor $\div(\psi(\Phi))$.

	The previous discussion shows that if $\Phi$ is not nilpotent and $\div(\psi(\Phi))$ is irreducible, then there are no $\Phi$-invariant line bundles $L\subseteq E$.
	By \Cref{lm:traceless} we have
	\[ h^{0}(M,\sEnd_{0}(\E)\ot \sK)\geqslant 3g-3\geqslant 3, \]
	so the complete linear system defined by the invertible sheaf $\pi^{*}(\sK\ot\Lambda^{2}\E)(2)$ has dimension at least $2$.
	If this linear system does not have a fixed divisor, then Bertini's theorem \cite[Theorem 7.19]{iit82} tells us that $\div(\psi(\Phi))$ is irreducible for a general $\Phi\in H^{0}(M,\sEnd_{0}(\E)\ot \sK)$.
	Since in our case $\Phi\in H^{0}(M,\sEnd_{0}(\E)\ot \sK)$ is nilpotent if and only if $\Phi^{2}=0$, a general $\Phi$ is not nilpotent.
	Therefore $E\in \bfA$ in this case.

	Let us see what happens if the linear system has a fixed divisor.
	Such a fixed divisor must be the zero locus of a non-zero global section $s$ of an invertible sheaf on $\P(E)$, which is up to isomorphism of the form $\pi^{*}\L(l)$ with $\L$ an invertible sheaf on $M$ and $l\in \Z$ \cite[Exercise II.7.9]{har77}.
	Being a fixed divisor means then that every other global section of our line bundle can be written as a product $st$, where $t\in H^{0}(\P(E),\pi^{*}\sN(2-l))$.
	Since our line bundle had non-zero global sections, both $\pi^{*}\L(l)$ and $\pi^{*}\sN(2-l)$ must have non-zero global sections.
	By the projection formula, this leaves us with only three possibilities:
	\begin{enumerate}[label=\alph*)]
	    \item $l=0$;
	    \item $l=1$;
	    \item $l=2$.
	\end{enumerate}
	We analyze each case separately to conclude that
	\[ E\in \begin{cases} \bfA & \text{ if }l=0, \\
	    \bfB & \text{ if }l\in \{1,2\}.
	\end{cases} \]

	\color{gray}
	Let us start with case $a)$.
	Let $\pi^{*}s\in H^{0}(\P(E),\pi^{*}\L)\cong H^{0}(M,\L)$ be a global section corresponding to the fixed component of our linear system.
	Dividing all global sections by $s$ and by $\pi^{*}s$ respectively we obtain the following commutative diagram:
	\begin{center}
	    \begin{tikzcd}
		H^{0}(M,\sEnd_{0}(\E)\ot \sK)\arrow{r}{\cong}\arrow[swap]{d}{/s}[swap]{\cong} & H^{0}(\P(E),\pi^{*}(\sK\ot \Lambda^{2}\E)(2))\arrow{d}{\cong}[swap]{/\pi^{*}s} \\
		H^{0}(M,\sEnd_{0}(\E)\ot \sK\ot \L\dual)\arrow{r}{\cong} & H^{0}(\P(E),\pi^{*}(\L\dual \ot \sK\ot \Lambda^{2}\E)(2))
	    \end{tikzcd}
	\end{center}
	By definition, the new linear system does not have any fixed divisors and has the same dimension.
	Hence we can apply Bertini to conclude that a generic $\Phi'\in H^{0}(M,\sEnd_{0}(\E)\ot \sK\ot \L\dual)$ does not have invariant line bundles, which in this case are defined as line bundles $N\subseteq E$ such that $\Phi'(N)\subseteq N\ot K\ot L\dual$.
	But a line bundle $N\subseteq E$ is $\Phi'$-invariant if and only if it is $s\Phi'$-invariant, so we have $E\in \bfA$ in this case.

	We move on to case $b)$.
	Assume that the fixed divisor corresponds to a non-zero global section $s\in H^{0}(\P(E),\pi^{*}\L(1))$.
	This corresponds to a non-zero morphism $E\to L$.
	The fiber-wise kernel has then dimension $1$ generically and $2$ at special points by upper semi-continuity \cite[Proposition 1.3.2]{ati89}.
	Let $N\subseteq E$ be the largest line subbundle of $E$ contained in the kernel of $s$.
	If $v\in N$ is a non-zero vector, then $s(v)=0$ and so $[v]\in \div(s)\subseteq \div(\psi(\Phi))$.
	Thus the corresponding section $\sigma(M)\subseteq \P(E)$ is contained in $\div(\psi(\Phi))$ for all $\Phi$ and $N$ is $\Phi$-invariant for all $\Phi$.
	Hence $E\in \bfB$ in this case.

	In case $c)$, the fixed divisor corresponds to a non-zero global section of $\pi^{*}\L(2)$.
	We have
	\[ H^{0}(\P(E),\pi^{*}\L(2))\cong H^{0}(M,\L\ot S^{2}\E\dual)\cong H^{0}(M,\sEnd_{0}(\E)\ot \L\ot \Lambda^{2}\E\dual). \]
	So we can think of the fixed global section $s$ as a traceless endomorphism of $E$ with coefficients in $L\ot \Lambda^{2}E\dual$.
	With this point of view, $s$-invariance of a line bundle $N\subseteq E$ translates into $s\Phi'$-invariance of $N\subseteq E$ as before, where $s\Phi'$ is a Higgs field.
	Let us see that the fixed section $s$ has some non-trivial kernel, hence defining a line bundle invariant under all Higgs fields as in the previous case.
	To show that there is some non-trivial kernel, it suffices to check that $\det(s)=0$.
	Since $s$ is traceless, it suffices in turn to check that $\tr(s^{2})=0$.
	Suppose on the contrary that $\tr(s^{2})\neq 0$.
	Fix some non-zero $s_{1}\in H^{0}(M,\L\dual\ot \sK\ot \Lambda^{2}\E)$ and consider the linear map
	\begin{align*}
	    \theta \colon H^{0}(M,\L\dual\ot\sK\ot \Lambda^{2}\E) & \longrightarrow H^{0}(M,\sK^{2}) \\
	    \Phi' & \longmapsto \tr(s^{2})s_{1}\Phi'
	\end{align*}
	Since $\tr(s^{2})s_{1}$ can only vanish at finitely many points, the image of a non-zero $\Phi'$ can only vanish at finitely many points, hence $\theta$ is injective.
	From Hirzebruch--Riemann--Roch and \Cref{lm:traceless} we know that
	\[ h^{0}(M,\L\dual\ot\sK\ot \Lambda^{2}\E)\geqslant 3g-3=h^{0}(M,\sK^{2}), \]
	so $\theta$ is an isomorphism.
	Since $\L\dual\ot \sK\ot \Lambda^{2}\E$ has global sections, its degree is non-negative.
	If it was zero, then this would be the trivial line bundle and we would have $h^{0}(M,\L\dual\ot\sK\ot\Lambda^{2}\E)=1<3g-3$, a contradiction.
	Hence $\deg(\L\dual\ot\sK\ot\Lambda^{2}\E)>0$ and the non-zero global section $s_{1}$ has at least one zero.
	If $\theta$ was indeed an isomorphism, then each zero of $s_{1}$ would give a base point of the complete linear system corresponding to $\sK^{2}$.
	But $\deg(\sK^{2})=4g-4\geqslant 2g$, so this linear system has no base points \cite[Corollary IV.3.2]{har77}.
	This contradiction shows that $s$ has non-trivial kernel, which contains a line bundle $N\subseteq E$ invariant by all $\Phi\in H^{0}(M,\sEnd_{0}(\E)\ot \sK)$.
	Hence $E\in \bfB$ as well in this case.
    \end{proof}
\end{lm}

\begin{cexe}{B}
    Assume $g\geqslant 2$.
    Let $K^{\frac{1}{2}}$ be a line bundle whose square is $K$ and let $K^{-\frac{1}{2}}$ be its inverse.
    Does $K^{\frac{1}{2}}\op K^{-\frac{1}{2}}$ belong to $\bfA$ or to $\bfB$?
    [\textit{Hints below}\footnote{Consider the family of traceless endomorphisms given by 
    $$\Phi_{\alpha}:=\begin{pmatrix} 0 & \alpha \\ 1 & 0 \end{pmatrix},$$
	parametrized by quadratic differentials $\alpha\in H^{0}(M,K^{2})$. Use without proof the fact that an invariant line bundle exists if and only if the characteristic polynomial
	$$\lambda^{2}-\alpha$$
	has a root in $H^{0}(M,K)$, i.e.~if and only if the quadratic differential $\alpha$ can be written as a square $\alpha=\beta^{2}$ for some differential form $\beta\in H^{0}(M,K)$. If $\alpha$ was a square, its zeros would all have multiplicity at least two. Conclude that $K^{\frac{1}{2}}\op K^{-\frac{1}{2}}\in \bfA$ using Bertini's theorem.}]
\end{cexe}

\begin{lm}\label{lm:linearalgebra}
    Let $E\in \Vec_{2}(M)$ and $L\subseteq E$ a line bundle.
    We have the following short exact sequences:
    \begin{enumerate}[label=\alph*)]
	\item $0\to \L^{2}\ot (\Lambda^{2}\E)\dual \ot \sK \to \sEnd_{0}(\E)\ot \sK\to \E\ot \L^{-1}\ot \sK\to 0$.
	\item $0\to \E\dual \ot \L\ot \sK\to \sEnd_{0}(\E)\ot \sK \to \L^{-2}\ot (\Lambda^{2}\E)\ot \sK\to 0$.
    \end{enumerate}
    Moreover, the non-zero sections of the image of $\L\ot (\Lambda^{2}\E\dual)\ot \sK$ in $a)$ leave only $L$ invariant; and the sections of the image of $\E\dual\ot \L\ot \sK$ in $b)$ are those which leave at least $L$ invariant.
    \color{gray}
    \begin{proof}
	All the short exact sequences are the result of tensoring another short exact sequence with $\sK$, so let us find the necessary short exact sequences without $\sK$.
	Under the isomorphism $E\cong E\dual \ot \Lambda^{2}E$ \cite[Exercise II.5.16]{har77}, the line bundle $L$ is sent to linear forms with coefficients in $\Lambda^{2}E$ vanishing along $L$, hence we have a short exact sequence
	\[ 0\to \L\to \E\to \L\dual \ot \Lambda^{2}\E\to 0. \]
	Dualizing this short exact sequence we obtain an inclusion $L\ot \Lambda^{2}E\dual \subseteq E\dual$.
	Tensoring with $L$ and composing with the inclusion $E\dual\ot L\subseteq E\dual \ot E$ we obtain an inclusion $L^{2}\ot \Lambda^{2}E\dual \subseteq \End(E)$.
	Choosing a basis on each fiber and chasing all the identifications we have made so far, we see that the image of $L^{2}\ot \Lambda^{2}E\dual$ lies actually in $\End_{0}(E)$.
	Indeed, let $V$ be a two dimensional $\C$-vector space and let $e_{1}$ and $e_{2}$ be a basis.
	Let $L$ be the line spanned by a non-zero vector $l$, which we may assume to be $e_{1}$.
	The first identification we have is $V\cong \Hom(V,\Lambda^{2}V)$, sending $v$ to the homomorphism $v'\mapsto v'\wedge v$.
	This corresponds to $\alpha_{v}\ot (e_{1}\wedge e_{2})\in V\dual\ot\Lambda^{2}V$, where $\alpha_{v}\in V\dual$ is the linear form sending $e_{1}\mapsto v_{2}$ and $e_{2}\mapsto -v_{1}$.
	Denoting by $\overline{\alpha_{v}}$ its image in $L\dual$, we can describe the morphism corresponding to the right hand side of the previous short exact sequence as
	\begin{align*}
	    V &\longrightarrow L\dual \ot \Lambda^{2}V \\
	    v &\longmapsto \overline{\alpha_{v}}\ot (e_{1}\wedge e_{2})
	\end{align*}
	Let now $\beta\in (L\dual \ot \Lambda^{2}V)\dual$ and denote by $\lambda_{v}^{\beta}$ the complex number such that
	\[ \overline{\alpha_{v}}\ot (e_{1}\wedge e_{2})\overset{\beta}{\longmapsto} \lambda_{v}^{\beta}. \]
	A point $\mu l\ot \beta\in L\ot (L\dual\ot \Lambda^{2}V)\dual$ corresponds then to the endomorphism
	\begin{align*}
	    V &\longrightarrow V \\
	    v &\longmapsto \mu \lambda_{v}^{\beta}l
	\end{align*}
	A basis for $L$ is $e_{1}$, a basis for $L\dual \ot \Lambda^{2}V$ is $\overline{\alpha_{e_{2}}}\ot (e_{1}\wedge e_{2})$ and a basis for $L\ot (L\dual\ot \Lambda^{2})\dual$ is $e_{1}\ot \beta_{0}$, where $\beta_{0}\in (L\dual \ot \Lambda^{2}V)\dual$ is such that $\lambda_{e_{2}}^{\beta_{0}}=1$.
	Writing the image of the basis $e_{1}\ot \beta_{0}$ under the map $L\ot (L\dual\ot \Lambda^{2}V)\dual\to \End(V)$ as a matrix with respect to our bases we obtain
	\[
	    \begin{pmatrix}
		0 & 1 \\
		0 & 0
	    \end{pmatrix},
	\]
	because $\overline{\alpha_{e_{1}}}=0$ and therefore $\lambda_{e_{1}}^{\beta}=0$ for any $\beta$.
	We have thus the desired injective homomorphism
	\[ L^{2}\ot \Lambda^{2}V\dual\hookrightarrow \End_{0}(V) \]
	whose image are the traceless endomorphisms which preserve only $L$.
	This is the morphism from which we obtain the short exact sequence in $a)$.

	We regard this as a homomorphism into $\End(V)$ for a moment and use the basis $e_{11},e_{12},e_{21},e_{22}$ of $\End(V)$, where $e_{ij}$ denotes the endomorphism which, represented as a matrix in terms of our basis, has zeros everywhere except for a $1$ in the $ij$-th position.
	Then our homomorphism is given by
	\[ 
	    \begin{pmatrix}
		0 \\
		1 \\
		0 \\
		0
	    \end{pmatrix}
	\]
	Dualizing it we obtain a surjection
	\[ \End_{0}(V\dual)\twoheadrightarrow L^{-2}\ot \Lambda^{2}V \]
	given with respect to the dual bases by
	\[
	    \begin{pmatrix}
		0 & 1 & 0 & 0
	    \end{pmatrix}.
	\]
	Its kernel are the endomorphisms of $V\dual$ represented with respect to the dual basis by a matrix of the form
	\[
	    \begin{pmatrix}
		a & 0 \\
		b & -a
	    \end{pmatrix}.
	\]
	Hence, under the isomorphism $\End(V)\cong \End(V\dual)$ given in coordinates by sending a matrix to its transpose, we obtain a surjection
	\[ \End_{0}(V)\twoheadrightarrow L^{-2}\ot \Lambda^{2}V \]
	whose kernel are endomorphisms represented with respect to our basis by matrices of the form
	\[
	    \begin{pmatrix}
		a & b \\
		0 & -a
	    \end{pmatrix}.
	\]
	Therefore the kernel of this surjection consists precisely of the traceless endomorphisms of $V$ that leave at least $L$ invariant.
	The inclusion of this kernel can be naturally regarded as the composition of the inclusion $\Hom(V,L)\subseteq \Hom(V,V)$ and the projection $\pr_{0}\colon \Hom(V,V)\to \End_{0}(V)$, which writing every homomorphism as a matrix with respect to the bases above has the form
	\[ 
	\begin{pmatrix}
	    a & b
	\end{pmatrix}
	\mapsto
	\begin{pmatrix}
	    a & b \\
	    0 & 0
	\end{pmatrix}
	\mapsto
	\begin{pmatrix}
	    \frac{a}{2} & b \\
	    0 & -\frac{a}{2}
	\end{pmatrix}.
	\]
	This gives us the short exact sequence in $b)$ and the right hand side of the short exact sequence in $a)$.
    \end{proof}
\end{lm}

\begin{lm}\label{lm:stable}
    If $g\geqslant 2$ and $E$ is a stable rank $2$ vector bundle, then $E\in \bfA$.
    \begin{proof}
	By \Cref{lm:twocases} it suffices to show that it is not in $\bfB$.
	So let $E$ be a stable rank $2$ vector bundle on $M$ and assume $L\subseteq E$ is a line bundle which is $\Phi$-invariant for all $\Phi\in H^{0}(M,\sEnd_{0}(\E)\ot \sK)$.
	Consider the short exact sequence $b)$ from \Cref{lm:linearalgebra}
	\[ 0\to \E\dual\ot \L\ot\sK\to \sEnd_{0}(\E)\ot \sK \to \L^{-2}\ot (\Lambda^{2}\E)\ot\sK\to 0. \]
	Since all $\Phi\in H^{0}(M,\sEnd_{0}(\E)\ot\sK)$ leave $L$ invariant, we get an induced isomorphism on global sections $H^{0}(M,\E\dual\ot\L\ot\sK)\cong H^{0}(M,\sEnd_{0}(\E)\ot \sK)$.
	The left hand side of the short exact sequence $a)$ in \Cref{lm:linearalgebra} factors by construction into a short exact sequence of the form 
	\[ 0\to \L^{2}\ot (\Lambda^{2}\E)\dual\ot\sK \to \E\dual \ot \L\ot \sK\to \sQ\ot\sK\to 0, \]
	where $\deg(\sQ)$ can be seen to be $0$ by computing first Chern classes.
	Riemann--Roch says then that $h^{0}(\sQ\ot\sK)\in \{g-1,g\}$.
	Since $E$ is stable, we have $\deg(\L^{2}\ot \Lambda^{2}\E\dual)<0$, and since the complete linear system corresponding to $\sK$ is base-point free \cite[Lemma IV.5.1]{har77}
	    we have $h^{0}(M,\L^{2}\ot(\Lambda^{2}\E)\dual\ot\sK)\leqslant g-1$ by \cite[Proposition IV.3.1]{har77}.
	The long exact sequence of the previous short exact sequence gives then
	\[ h^{0}(M,\E\dual\ot\L\ot\sK)\leqslant 2g-1. \]
	The earlier Hirzebruch--Riemann--Roch computation showed that
	\[ h^{0}(M,\sEnd_{0}(\E)\ot \sK)\geqslant 3g-3. \]
	If we want the two dimensions to be equal we must have $g=2$ and $h^{0}(M,\sK\ot\L\ot\E\dual)=3$.
	From the same long exact sequence as before we deduce, using that $h^{0}(M,\L^{2}\ot (\Lambda^{2}\E)\dual\ot \sK)<g=2$, that $h^{0}(M,\L^{2}\ot(\Lambda^{2}\E)\dual\ot\sK)=1$.
	In particular, $\deg(\L^{2}\ot(\Lambda^{2}\E)\dual\ot\sK)\geqslant 0$.
	We have $\deg(\sK)=2$ and by stability we had $\deg(\L^{2}\ot \Lambda^{2}\E\dual)<0$, so we must have
	\[ \deg(\L^{2}\ot (\Lambda^{2}\E)\dual\ot\sK)\in \{0,1\}. \]
	We treat each case separately, showing that both of them lead to contradiction.

	\color{gray}
	If it is $0$, then the existence of global sections implieis that it is the trivial line bundle, hence the previous short exact sequence becomes
	\[ 0\to \O\to \E\dual\ot\L\ot\sK\to \sK\to 0. \]
	Split short exact sequences are preserved by dualizing and tensoring with line bundles, so if this sequence was split then $\E$ would be decomposable as a direct sum of line bundles.
	But this would give more endomorphisms of $\E$ than there should be, since stable vector bundles are simple.
	So the previous short exact sequence is a non-trivial extension, hence its extension class $\xi$, defined as the image of $\1_{\sK}$ under the coboundary map $\delta\colon \Hom(\sK,\sK)\to \Ext^{1}(\sK,\O)$, is non-zero \cite[Exercise III.6.1]{har77}.
	The coboundary map $H^{0}(M,\sK)\to H^{1}(M,\O)$ is given by cup product with $\xi\in H^{1}(M,\sT_{M})$ \cite[Theorem II.7.1]{bre97}.
	Hence it is non-zero, and the long exact sequence implies then that $h^{0}(M,\E\dual\ot \sK\ot\L)\leqslant 2$, contradicting our previous conclusion that this dimension was $3$.

	If it is $1$, again by the existence of a non-zero global secction we deduce that it is the line bundle corresponding to some point $x\in M$.
	The short exact sequence becomes
	\[ 0\to \O(x)\to \E\dual\ot\L\ot\sK\to \sK\to 0, \]
	and the extension class $\xi\in H^{1}(M,\sK^{-1}(x))$ is again non-zero.
	Let $s\in H^{0}(M,\sK(-x))$ be a non-zero global section, which exists because subtracting a point makes the dimension of the space of global sections go down at most by one, and in this case precisely by one by base point freeness.
	Since $h^{0}(M,\sK)=h^{0}(M,\sK^{2}(-x))$, we can write every section in $H^{0}(M,\sK^{2}(-x))$ as $st$ for some $t\in H^{0}(M,\sK)$.
	By Serre duality, the cup product gives us a perfect pairing
	\[ H^{0}(M,\sK^{2}(-x))\times H^{1}(M,\sK^{-1}(x))\to H^{1}(M,\sK)\cong \C. \]
	Since $\xi\neq 0$, we can find some $st\in H^{0}(M,\sK^{2}(-x))$ such that $st\cup \xi\neq 0$.
	But the cup product is associative \cite[Proposition II.7.3]{bre97} and the product of section $st$ is by definition their cup product, so we must have $t\cup \xi\neq 0$.
	Therefore the coboundary map $\delta\colon H^{0}(M,\sK)\to H^{1}(M,\O)$ is non-zero, because it is given by cup product with $\xi$ \cite[Theorem II.7.1]{bre97} and so $\delta(t)=t\cup \xi \neq 0$.
	This contradicts again our previous conclusion that $h^{0}(M,\E\dual\ot \L\ot \sK)=3$.
    \end{proof}
\end{lm}

\begin{prop}\label{prop:general}
    If $g\geqslant 2$, then
    \[ \bfS=\bfA. \]
    \begin{proof}
	By definition $\bfA\subseteq \bfS$, so let us see the other inclusion.
	Let $E\in \bfS$.
	If $E$ is stable, then $E\in \bfA$ by \Cref{lm:stable}.
	So assume there exists $L\subseteq E$ such that $\mu(L)\geqslant \mu(E)$.
	Then $\deg(\L^{2}\ot(\Lambda^{2}\E)\dual\ot\sK)\geqslant 2g-2$, so Riemann--Roch implies that $h^{0}(\L^{2}\ot(\Lambda^{2}\E)\dual\ot\sK)\in \{g-1,g\}$.
	In particular, from the short exact sequence $a)$ in \Cref{lm:linearalgebra} we deduce that there exists a non-zero Higgs field leaving only $L$ invariant.
	So if $E\in \bfB$, then this $L$ is a line bundle invariant by all $\Phi\in H^{0}(M,\sEnd_{0}(\E)\ot \sK)$.
	Since $\mu(L)\geqslant \mu(E)$, this contradicts the assumption that $E\in \bfS$.
    \end{proof}
\end{prop}

\textcolor{gray}{%
Summarizing what we have seen in this first section, if $M$ is a compact Riemann surface of genus $g\geqslant 2$ and $E$ is a rank $2$ vector bundle on $M$, then there are only two mutually exclusive possibilities:
    \begin{itemize}
	\item A general section $\Phi\in H^{0}(M,\sEnd_{0}(\E)\ot \sK)$ leaves no line bundle $L\subseteq E$ invariant.
	\item There exists a line bundle $L\subseteq E$ which is invariant under all sections $\Phi\in H^{0}(M,\sEnd_{0}(\E)\ot \sK)$.
    \end{itemize}
    Moreover, $E$ appears in a stable pair $(E,\Phi)$ if and only if a general section $\Phi\in H^{0}(M,\sEnd_{0}(\E)\ot\sK)$ leaves no line bundle $L\subseteq E$ invariant.
}

\section{Idea of the existence theorem}

\begin{unota}
    From now on, all vector bundles, morphisms and sections are only assumed to be smooth unless otherwise stated.
    We follow the notation in \cite{kob87} for differential forms, e.g.~$A^{p,q}(E)$ denotes the space of $(p,q)$-forms over $M$ with values in $E$.
\end{unota}

Let $E\to M$ be a complex vector bundle of rank $2$ and let $h$ be a Hermitian metric on $E$.
Let $\sA_{E}$ denote the space of unitary connections on $E$.
Our goal is to find a solution $(\nabla,\Phi)\in N:=\sA_{E}\times A^{1,0}(\End_{0}(E))$ to \Cref{eqn:hitchin} starting from a stable Higgs bundle $(E,\Phi)$.

\textcolor{gray}{%
We can endow $N$ with a Kähler structure given by
\[ \w((A_{1},\Phi_{1}),(A_{2},\Phi_{2}))=-\int_{M}\tr(A_{1}\wedge A_{2})+2i\Im(\tr(\Phi_{1}\Phi_{2}^{*})) \]
for $A_{1},A_{2}\in A^{1}(\u_{h}(E))$ and $\Phi_{1},\Phi_{2}\in A^{1,0}(\End_{0}(E))$, where $\u_{h}(E)$ is the vector bundle of skew-hermitian endomorphisms of $E$ \cite[Corollary 4.2.11]{huy05}.
}

The gauge group $\G=A^{0}(\U_{h}(E))$ of unitary automorphisms of $E$ acts on $N$ by conjugation on each factor, and this action admits a moment map
\[ \mu(\nabla,\Phi)=-F-[\Phi,\Phi^{*}]-2\pi i \mu(E)\1_{E}\w_{M}. \]

Let then $(\nabla_{0},\Phi_{0})\in N$ be a stable Higgs bundle, where $\nabla_{0}=\nabla(\bar{\partial}_{E})$ is the Chern connection of the given holomorphic structure $\bar{\partial}_{E}$ on $E$.
The complex gauge group $\G^{c}_{0}$ of automorphisms of $E$ with determinant $1$ acts on $N$ as well, sending $(\nabla,\Phi)$ to $(\nabla(g\nabla^{0,1}g^{-1}),g\Phi g^{-1})$.
In particular, $\Phi$ remains a holomorphic section with respect to the new $\bar{\partial}_{E}=\nabla^{0,1}$.
Moreover, $\G^{c}_{0}$ acts freely on the orbit of the stable Higgs bundle $(\nabla_{0},\Phi_{0})$ by proposition \cite[(3.15)]{hit87a} from Jin's talk.
It follows from this and the discussion in \cite[\S 4]{hit87a} or in \cite[\S 8]{ab83} that if we manage to find a minimum of for
\[ f(\nabla,\Phi):=\int_{M}||\mu(\nabla,\Phi)||^{2} \]
in the orbit of $(\nabla_{0},\Phi_{0})$, we will have solved \Cref{eqn:hitchin}.

To do this, we pick a minimizing sequence $(\nabla_{n},\Phi_{n})$ for $f$ in the orbit of $(\nabla_{0},\Phi_{0})$.
This is always possible by definition of infimum and convexity of $f$ \cite[\S 8]{ab83}.
After some analysis we can apply Uhlenbeck's theorem, which allows us to assume that $(\nabla_{n},\Phi_{n})$ has a weakly convergent subsequent.
We have to show that its limit $(\nabla,\Phi)$ is still in the same $\G^{c}_{0}$-orbit of $(\nabla_{0},\Phi_{0})$.
Let $\psi_{n}\in \G^{c}_{0}$ map $(\nabla_{n},\Phi_{n})$ to $(\nabla_{0},\Phi_{0})$.
Doing some more analysis, we may assume that the sequence $\psi_{n}$ is weakly convergent, having then a non-zero limit $\psi$ \cite[p.~82]{hit87a}.
By definition we have identities
\[ \nabla_{(n,0)}^{0,1}\psi_{n}=0 \text{ and } \Phi_{0}\psi_{n}=\psi_{n}\Phi_{n}, \]
where $\nabla_{(n,0)}$ denotes the connection induced by $\nabla_{n}$ and $\nabla_{1}$ on $\End(E)$ \cite[Example 4.2.6 iii)]{huy05}.
These remain true in the limit, so $\psi$ is a holomorphic morphism from $(E,\nabla^{0,1})$ to $(E,\nabla^{0,1}_{0})$ such that $\Phi_{0}\psi=\psi\Phi$.
But $\psi$ is non-zero, so we have the following two possibilities:
\begin{itemize}
    \item $\psi$ is an isomorphism, in which case it is in $\G^{c}_{0}$ and $(\nabla,\Phi)$ is in the same orbit as $(\nabla_{0},\Phi_{0})$, yielding the desired solution.
    \item The image of $\psi$ has generically rank $1$, going down to $0$ only at special points by upper-semicontinuity \cite[Proposition 1.3.2]{ati89}.
\end{itemize}

Assume then that we are in the second case.
Since $\psi$ is holomorphic, the saturation of $\psi(E)$ in $E$ defines a line bundle $L\subseteq E$ holomorphic with respect to $\nabla_{0}^{0,1}$.
But $\Phi_{0}\psi=\psi\Phi$, so $L$ is $\Phi_{0}$-invariant.
\textcolor{gray}{%
Indeed, it suffices to check this generically, so let $x\in M$ such that $L_{x}=\psi(E_{x})$ and let $v=\psi(v')\in L_{x}$.
Then $\phi_{0}(v)=\phi_{0}(\psi(v'))=\psi(\phi(v'))\in \psi(E_{x})$.
}
By \Cref{prop:general}, since $(\nabla_{0},\Phi_{0})$ is stable, this is impossible for $\Phi_{0}$ on a non-empty Zariski open subset.
So for a general $\Phi_{0}$, the limit $\psi$ had to be an isomorphism.

The general non-general case will follow from a further application of Uhlenbeck's theorem.

\bibliographystyle{alpha}
\bibliography{main}
\vfill

\end{document}
